---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# instaquote

<!-- badges: start -->
<!-- badges: end -->

The goal of instaquote is to make it easy to plot quotes in an image so that
you can export them to instagram/social media or in R markdown.

## Installation

<!--
You can install the released version of instaquote from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("instaquote")
```
And the development version from [GitHub](https://github.com/) with:
-->

You can install the development version from [GitHub](https://github.com/bryanwhiting/instaquote) with:

``` r
# install.packages("devtools")
devtools::install_github("bryanwhiting/instaquote")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(instaquote)
## basic example code
txt <- 'hello world'
instaquote(txt)
```

Notice the watermark `gospelanalysis.com`. If anyone else besides me 
uses this package, I'm happy to remove that. I just built it into the default
option.

You can customize with html:
```{r example2}
txt <- '**hello** <span style="color:red">world</span>'
instaquote(txt, bg_color='black')
```

Generate custom text:

```{r example3}
txt <- insta_text(
  title = '**Cool** _title_', 
  subtitle = 'A **really** long subtitle that will eventually wrap if I write enough words on it. it also _supports_ **markdown** and <span style="color:pink">html</span>.')
instaquote(txt)
```

# Kudos

* `ggtext` and `ggplot2` power this project. Thanks to the awesome authors
of those packages!
